Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-01-30 main.tex
Updates from ShareLaTeX

In this article we compare the results of our inversion with a number of previous tomographic models.
On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
which is an updated version of model S362ANI~\citep{s362ani},
the starting model for the GLAD-M15 inversion.
We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
and SL2013sv~\citep{SchaefferLebedev13},
as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
On the scale of North America,
we make comparisons with models US22~\citep{zhu2017radial},
a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
and SL2013NA~\citep{schaeffer2014imaging},
a modification of global model SL2013sv focused on North America.
In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227 earthquakes recorded by more than 1,800 stations.

This article is organized as follows.
Sections~\ref{section:start}--\ref{section:data} describe the starting model,
earthquake database, and seismographic data set. 
Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
and the related model parameterization.
In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
Sections~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 320 earthquakes.
Finally, in Section~\ref{section:model}, we describe the model in detail,
offering many comparisons with various global and regional models, as described in the proceeding paragraph.
We conclude with a discussion of future opportunities and directions.

@@

As a continuation of our previous work~\citep{bozdaug2016global},
we used first-generation model GLAD-M15 as our
starting model.
GLAD-M15 is a 3D transversely isotropic earth model, which combined
3D mantle model S362ANI~\citep{kustowski2008anisotropic}
with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
In this study,
we continue to use the same transversely isotropic model parametrization.
Instead of relying on ubiquitous ``crustal corrections'',
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
GLAD-M15 was constructed using a global database of 256 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{Source corrections for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  }
  \label{fig:source_correction}
\end{figure}

@@

The algorithm inverts for the six elements of the moment tensor
and the centroid location~(latitude, longitude, and depth).
These source inversions are computationally very expensive,
because for each of the 1,040~events, nine full 3D forward simulations are required.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_1480.pdf}
  \caption{The 1,480~earthquakes used in this study. (a) Distribution of earthquakes. The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km. (b) \& (c) Histograms of earthquake moment magnitudes and depths.}
  \label{fig:event_1480}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
  \caption{Distribution of the 11,800~seismographic stations used in this study. Colors denote the number of events for which a given station contributes waveforms to the structural inversion. Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers. The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}
  \label{fig:stations}
  \centering
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
  \caption{Adjoint tomography workflow.}
  \label{fig:adjoint_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
  \caption{Sub-workflow workflow for preprocessing seismic data.}
  \label{fig:preprocess_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 1,375--1,376~sec time bin.
  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }
  \label{fig:window_density_Z}
\end{figure}

@@

To illustrate which seismic phases end up being picked,
Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and \ref{fig:window_density_T} show time-distance plots
for vertical, radial, and transverse component 17--40~s body waves,
respectively,
in which the Pyflex window count is used to identify parts of seismograms being assimilated.
The figures nicely highlight all the well known body traveltime branches.
The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
This is something we will reconsider in future applications, perhaps by introducing aspects of machine learning.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~sec time bin.
   }
  \label{fig:window_density_R}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~sec time bin.
   Only SH travetime branches are labeled.}
  \label{fig:window_density_T}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/misfit.pdf}
  \caption{Evolution of the misfit function from GLAD-M15 to GLAD-M25.
  Each color denotes different stages of the inversion, as discussed in Sections~\ref{sec:I}--\ref{sec:III}.
  (a) Evolution of the total misfit. (b)--(j) Misfit in
  each period band (rows) on three components (columns). (e)--(g) At iteration 18,
  we  split the 40--100~s period band into two
  measurement categories: body waves (red diamonds) and surface waves
  (red squares).
  }
  \label{fig:misfit}
\end{figure}

@@

% \begin{table}[!htb]
%   \centering
%   \begin{tabular}{|c|c|c|c|}
%     \hline
%     ~          &  Vertical & Radial &  Transverse \\
%     \hline
%     17--40~s   &   P-SV          & P-SV           & SH   \\
%     40--100~s  &   P-SV          & P-SV            & SH \\
%     40--100~s  &   Rayleigh   & Rayleigh    & Love \\
%     90--250~s  &   All                 & All                  & All  \\
%     \hline
%   \end{tabular}\\
%   \caption{Twelve measurement categories used for iterations 18--25.
%   Before iteration~18, the 40--100~s body and surface waves categories were combined into a single category on each component, resulting in nine categories.}
%   \label{table:measurement_category}
% \end{table}

@@

\begin{table}[!htb]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
    \hline
    %17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
    %40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
    %40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
    %90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
    17--40~s  body waves    &   19.1 (37.3)   &       23.7 (46.3) &       28.2 (54.8) \\
    40--100~s body waves    &   18.3 (37.5)   &       24.0 (51.4) &       24.5 (54.5) \\
    40--100~s surface waves &   33.6 (69.6)   &       33.3 (71.5) &       33.5 (77.2) \\
    90--250~s all waves &   15.7 (44.9)   &       14.4 (49.1) &       29.6 (48.7) \\
    \hline
  \end{tabular}\\
  \caption{Changes in fit in the twelve measurement categories
  between the new model, GLAD-M25, and its starting model, GLAD-M15,
  and, in parentheses, between GLAD-M25 and model S362ANI combined with
  CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
  \label{table:misfit_reduction_M15_M25}
\end{table}

% \begin{table}[!htb]
%   \centering
%   \begin{tabular}{|c|c|c|c|}
%     \hline
%      ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
%     \hline
%     17--40s body waves     &    31.1    &       37.1 &       42.2 \\
%     40--100s body waves    &    31.3    &       40.2 &       42.0 \\
%     40--100s surface waves &    50.1    &       51.1 &       53.8 \\
%     90--250s               &    36.2    &       38.8 &       38.6 \\
%     \hline
%   \end{tabular}\\
%   \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
%   \label{table:misfit_reduction_M00_M25}
% \end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
  \caption{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
  Each column represents one component and each row corresponds to a period band.
  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
  The total number of measurements is 18.2 million.
  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}
  \label{fig:phase_hist}
\end{figure}

Fig.~\ref{fig:P_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components.
Both components exhibit consistent reductions in terms of both mean and variance. 
Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
  \caption{Histograms of 17--40~s traveltime anomalies of P arrival(Vertical and Radial), and SH arrival(Transverse) for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
  }
  \label{fig:PS_phase_hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
  \caption{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}
  \label{fig:amp_hist}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{Summary of the held-out database containing 360 earthquakes. Theses events were not used in the structural inversion. (a) Distribution of events color coded by depth range as in Fig.~\ref{fig:event_1480}. (b) \& (c) Histograms of moment magnitude and depth.}
  \label{fig:events_360}
\end{figure}

@@

\begin{table}[!htb]
  \centering
  %\label{tab:category}
  \begin{tabular}{|c|c|c|c|}
  \hline
  ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
  \hline
  17--40~s                &          11.8 (29.2) &       14.1 (33.7) &       21.5 (43.4) \\
  40--100~s body waves    &          14.5 (26.2) &       12.9 (32.2)  &       16.9 (39.0) \\
  40--100~s surface waves &          29.3 (49.1) &       28.1 (49.4) &       23.7 (51.2) \\
  90--250~s               &          10.9 (30.9) &       14.3 (34.8)  &       24.0 (34.9) \\
  \hline
  \end{tabular}\\
  \caption{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
  \label{table:misfit_reduction_M15_M25_360}
\end{table}

% \begin{table}[!htb]
%   \centering
%   %\label{tag:misfit_reduction_M00_M25_360}
%   \begin{tabular}{|c|c|c|c|}
%     \hline
%     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
%     \hline
%     17--40s                &         29.2 &       33.7 &       43.4 \\
%     40--100s body waves    &         26.2 &       32.2 &       39.0 \\
%     40--100s surface waves &         49.1 &       49.4 &       51.2 \\
%     90--250s               &         30.9 &       34.8 &       34.9 \\
%     \hline
%   \end{tabular}\\
%   \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out data set}
%   \label{table:misfit_reduction_M00_M25_360}
% \end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
  \caption{Same as Fig.~\ref{fig:phase_hist}, except for the held-out database.
  }
  \label{fig:phase_hist_360}
\end{figure}

P phase measurements were also extracted and compared in Fig.~\ref{fig:phase_hist_360_P} for 3 models. The behavior is consistent as we expected.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
  \caption{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}
  \label{fig:phase_hist_360_P}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
  \caption{Map views of global shear wavespeed perturbations at various depths for  model
  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
  At a given radius,
  perturbations are calculated relative to each model's average.
  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
  The green circles denote locations of various
  hotspots~\citep{montelli2006catalogue}.
  The range of the colorbar is the same for each row,
  and its maximum value is indicated in parentheses on the left, after
  the depth.}
  \label{fig:global-vs}
\end{figure}

%\begin{figure}
%\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
%  \caption{Map views of global $V_\textrm{P}$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}. For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing. Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
%\label{fig:global-vp}
%\centering
%\end{figure

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
  \caption{Map views of global compressional wavespeed variations at various depths for model
  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl}, and
  GAP-P4~\citep[right column;][]{fukao2013subducted}.
  For LLNL-G3Dv3, depth ranges are labeled in the bottom right
  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}
\label{fig:global-vp}
\centering
\end{figure}

@@

>>>>

In this article we compare the results of our inversion with a number of previous tomographic models.
On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
which is an updated version of model S362ANI~\citep{s362ani},
the starting model for the GLAD-M15 inversion.
We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
and SL2013sv~\citep{SchaefferLebedev13},
as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
On the scale of North America
we make comparisons with models US22~\citep{zhu2017radial},
a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
and SL2013NA~\citep{schaeffer2014imaging},
a modification of global model SL2013sv focused on North America.
In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227 earthquakes recorded by more than 1,800 stations.

This article is organized as follows.
Sections~\ref{section:start}--\ref{section:data} describe the starting model,
earthquake database, and seismographic data set. 
Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
and the related model parameterization.
In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 320 earthquakes.
Finally, in Section~\ref{section:model}, we describe the model in detail,
offering many comparisons with various global and regional models, as described in the proceeding paragraph.
We conclude with a discussion of future opportunities and directions.

@@

As a continuation of our previous work~\citep{bozdaug2016global},
we used first-generation model GLAD-M15 as our
starting model.
GLAD-M15 is a 3D transversely isotropic earth model, which combined
3D mantle model S362ANI~\citep{kustowski2008anisotropic}
with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
In this study,
we continue to use the same transversely isotropic model parametrization.
Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
GLAD-M15 was constructed using a global database of 256 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{\small{Source corrections for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  }}
  \label{fig:source_correction}
\end{figure}

@@

The algorithm inverts for the six elements of the moment tensor
and the centroid location~(latitude, longitude, and depth).
These source inversions are computationally very expensive,
because for each of the 1,040~events nine full 3D forward simulations are required.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_1480.pdf}
  \caption{\small{The 1,480~earthquakes used in this study. (a) Distribution of earthquakes. The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km. (b) \& (c) Histograms of earthquake moment magnitudes and depths.}}
  \label{fig:event_1480}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
  \caption{\small{Distribution of the 11,800~seismographic stations used in this study. Colors denote the number of events for which a given station contributes waveforms to the structural inversion. Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers. The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}}
  \label{fig:stations}
  \centering
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
  \caption{\small{Adjoint tomography workflow.}}
  \label{fig:adjoint_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
  \caption{\small{Sub-workflow workflow for preprocessing seismic data.}}
  \label{fig:preprocess_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{\small{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 1,375--1,376~sec time bin.
  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }}
  \label{fig:window_density_Z}
\end{figure}

@@

To illustrate which seismic phases end up being picked,
Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and \ref{fig:window_density_T} show time-distance plots
for vertical, radial, and transverse component 17--40~s body waves,
respectively,
in which the Pyflex window count is used to identify parts of seismograms being assimilated.
The figures nicely highlight all the well known body traveltime branches.
Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are of great importance, because they help constrain the compressional wavespeed structure in the model.
The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
This is something we will reconsider in future applications, perhaps by introducing aspects of machine learning.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~s time bin.
   }}
  \label{fig:window_density_R}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
  \caption{\small{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~s time bin.
   Only SH travetime branches are labeled.}}
  \label{fig:window_density_T}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/misfit.pdf}
  \caption{\small{Evolution of the misfit function from GLAD-M15 to GLAD-M25.
  Each color denotes different stages of the inversion, as discussed in Sections~\ref{sec:I}--\ref{sec:III}.
  (a) Evolution of the total misfit. (b)--(j) Misfit in
  each period band (rows) on three components (columns). (e)--(g) At iteration 18,
  we  split the 40--100~s period band into two
  measurement categories: body waves (red diamonds) and surface waves
  (red squares).
  }}
  \label{fig:misfit}
\end{figure}

@@

% \begin{table}[!htb]
%   \centering
%   \begin{tabular}{|c|c|c|c|}
%     \hline
%     ~          &  Vertical & Radial &  Transverse \\
%     \hline
%     17--40~s   &   P-SV          & P-SV           & SH   \\
%     40--100~s  &   P-SV          & P-SV            & SH \\
%     40--100~s  &   Rayleigh   & Rayleigh    & Love \\
%     90--250~s  &   All                 & All                  & All  \\
%     \hline
%   \end{tabular}\\
%   \caption{\small{Twelve measurement categories used for iterations 18--25.
%   Before iteration~18, the 40--100~s body and surface waves categories were combined into a single category on each component, resulting in nine categories.}}
%   \label{table:measurement_category}
% \end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
    \hline
    %17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
    %40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
    %40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
    %90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
    17--40~s  body waves    &   19.1 (37.3)   &       23.7 (46.3) &       28.2 (54.8) \\
    40--100~s body waves    &   18.3 (37.5)   &       24.0 (51.4) &       24.5 (54.5) \\
    40--100~s surface waves &   33.6 (69.6)   &       33.3 (71.5) &       33.5 (77.2) \\
    90--250~s all waves &   15.7 (44.9)   &       14.4 (49.1) &       29.6 (48.7) \\
    \hline
  \end{tabular}\\
  \caption{\small{Changes in fit in the twelve measurement categories
  between the new model, GLAD-M25, and its starting model, GLAD-M15,
  and, in parentheses, between GLAD-M25 and model S362ANI combined with
  CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
  \label{table:misfit_reduction_M15_M25}
\end{table}

% \begin{table}[!htb]
%   \centering
%   \begin{tabular}{|c|c|c|c|}
%     \hline
%      ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
%     \hline
%     17--40s body waves     &    31.1    &       37.1 &       42.2 \\
%     40--100s body waves    &    31.3    &       40.2 &       42.0 \\
%     40--100s surface waves &    50.1    &       51.1 &       53.8 \\
%     90--250s               &    36.2    &       38.8 &       38.6 \\
%     \hline
%   \end{tabular}\\
%   \caption{\small{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion.}}
%   \label{table:misfit_reduction_M00_M25}
% \end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram.pdf}
  \caption{\small{Histograms of phase measurements in all twelve measurement categories for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
  Each column represents one component and each row corresponds to a period band.
  The numbers above the top right of each panel denote the number of measurements in the corresponding category.
  The total number of measurements is 18.2 million.
  The mean and standard deviations of the phase measurements for the three models are displayed in the top right corner of each panel.}}
  \label{fig:phase_hist}
\end{figure}

Fig.~\ref{fig:PS_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components, and 17-40~s S-wave traveltime anomalies on the transverse component.
Both P and S waves exhibit consistent reductions in terms of both mean and variance.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
  \caption{\small{Histograms of 17--40~s traveltime anomalies of P (vertical and radial), and SH (Transverse) arrivals for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
  }}
  \label{fig:PS_phase_hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dlna_histogram.pdf}
  \caption{\small{Same as Fig.~\ref{fig:phase_hist} except for amplitude measurements. These measurements are currently not used in the inversion.}}
  \label{fig:amp_hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{\small{Summary of the held-out database containing 360 earthquakes. Theses events were not used in the structural inversion. (a) Distribution of events color coded by depth range as in Fig.~\ref{fig:event_1480}. (b) \& (c) Histograms of moment magnitude and depth.}}
  \label{fig:events_360}
\end{figure}

@@

@@

\begin{table}
  \centering
  %\label{tab:category}
  \begin{tabular}{|c|c|c|c|}
  \hline
  ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
  \hline
  17--40~s                &          11.8 (29.2) &       14.1 (33.7) &       21.5 (43.4) \\
  40--100~s body waves    &          14.5 (26.2) &       12.9 (32.2)  &       16.9 (39.0) \\
  40--100~s surface waves &          29.3 (49.1) &       28.1 (49.4) &       23.7 (51.2) \\
  90--250~s               &          10.9 (30.9) &       14.3 (34.8)  &       24.0 (34.9) \\
  \hline
  \end{tabular}\\
  \caption{\small{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
  \label{table:misfit_reduction_M15_M25_360}
\end{table}

% \begin{table}[!htb]
%   \centering
%   %\label{tag:misfit_reduction_M00_M25_360}
%   \begin{tabular}{|c|c|c|c|}
%     \hline
%     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
%     \hline
%     17--40s                &         29.2 &       33.7 &       43.4 \\
%     40--100s body waves    &         26.2 &       32.2 &       39.0 \\
%     40--100s surface waves &         49.1 &       49.4 &       51.2 \\
%     90--250s               &         30.9 &       34.8 &       34.9 \\
%     \hline
%   \end{tabular}\\
%   \caption{\small{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out data set.}}
%   \label{table:misfit_reduction_M00_M25_360}
% \end{table}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
  \caption{\small{Same as Fig.~\ref{fig:phase_hist}, except for the held-out database.
  }}
  \label{fig:phase_hist_360}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
  \caption{\small{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}}
  \label{fig:phase_hist_360_P}
\end{figure}

@@

Finally,
direct P and S traveltime anomaly measurements were extracted and compared for three models in Fig.~\ref{fig:phase_hist_360_P}.
Again the histograms are consistent with the actual inversion,
as expected.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
  \caption{\small{Map views of global shear wavespeed perturbations at various depths for  model
  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
  At a given radius,
  perturbations are calculated relative to each model's average.
  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
  The green circles denote locations of various
  hotspots~\citep{montelli2006catalogue}.
  The range of the colorbar is the same for each row,
  and its maximum value is indicated in parentheses on the left, after
  the depth.}}
  \label{fig:global-vs}
\end{figure}

@@

%\begin{figure}
%\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
%  \caption{\small{Map views of global $V_\textrm{P}$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}. For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing. Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}}
%\label{fig:global-vp}
%\centering
%\end{figure

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
  \caption{\small{Map views of global compressional wavespeed variations at various depths for model
  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl}, and
  GAP-P4~\citep[right column;][]{fukao2013subducted}.
  For LLNL-G3Dv3, depth ranges are labeled in the bottom right
  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}}
\label{fig:global-vp}
\centering
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
  \caption{\small{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
  one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
  bar is 4\% at all depths, as indicated in the bottom right bottom of the panels.}}
\label{fig:europe-vs}
\centering
\end{figure}
